SoK: The Evolution of Web Application Attack Defenses

### 2014-10-23 docs/questioning.tex
abstract draft, some rearrangements

@@

\begin{IEEEkeywords}
Security and Protection, Application Security, Code injection Attacks, Cyber Security Experiments, Effectivenes, Efficiency.
\end{IEEEkeywords}

@@

\section{Attacks and Background}
\label{sec:attacks}

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks that involve code injection ({\sc draft}).}
\end{figure*}

\section{Methodological Background}

@@

@@

%\tbl{Performance of System Prototype. Time is Measured in $\mu$s.}{

>>>>

In this paper we first systematize the existing knowledge
regarding the various defense mechanisms by setting up
a model for application attacks that are based on
source code injection vulnerabilities. This model
highlights the key weakness behind such attacks
and helps us observe defenses from a common
perspective.

We then categorize and analyze the various
defense mechanisms that have been developed.
Our analysis is based on dimensions such as accuracy,
performance, deployment and security.
Especially notable for a key category is accuracy,
as our findings show that there are many
defense mechanisms that are tested in a poor manner.

By comparing the existing defenses and identifying their
common characteristics, we help: a) researchers
and practitioners to choose or modify a mechanism
according to their needs, and b) designers of
new approaches in developing more efficient mechanisms.
% @dimitro: change the above accordingly.

@@

\begin{IEEEkeywords}
Security and Protection, Application Security, Code injection Attacks.
\end{IEEEkeywords}

@@

\section{Background}
\label{sec:attacks}

@@

\section{Dimensions of Study}

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.53]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on code injection vulnerabilities
({\sc draft}).}
\end{figure*}

The mechanism based on this method compare the parse tree of a
query before the inclusion of user input with the one resulting after
the inclusion of user input. If the trees diverge, the application
is probably under attack.

@@
